Hemodynamic responses of the anterior "parahippocampal place area" (PPA) to a Hollywood movie's audio-description

### 2020-12-11 paper/main.tex
changes to discussion of anterior vs posterior 1

% intro
Results of the AO contrasts consistently yielded significant clusters spatially
constrained to the anterior part of the PPA group overlap [and to the anterior
part of significant clusters of the AV contrasts].
% PPA might have submodules
Previous studies provide evidence that the posterior PPA (pPPA) and anterior PPA
(aPPA) show differences in both functional connectivity profiles and in response
to low- and high-level visual features.

% posterior connectivity
The pPPA is more strongly functionally connected to the occipital visual cortex
\citep{baldassano2013differential, baldassano2016two}.
% including lateral occipital cortex (LOC) and transverse occipital sulcus (TOS)
% functionality
Moreover, the pPPA is functionally more responsive than the aPPA to low-level
features of scenes or (abstract) objects \citep{baldassano2013differential,
nasr2014thinking, rajimehr2011parahippocampal}.

% anterior
The aPPA is more strongly functionally connected to portions of the default mode
network, including caudal inferior parietal lobe (cIPL), the restrosplenial
complex (RSC), medial PFC and the lateral surface of the anterior temporal lobe
\citep{baldassano2013differential, baldassano2016two}
% anterior cIPL is defined using the Eickhoff–Zilles PGp probabilistic
% cytoarchitectonic map
Moreover, the aPPA is functionally more responsive than pPPA to high-level
features of scenes (e.g. real-word size \citep{park2015parametric}; a scene's
abstract identity/category \citep{marchette2015outside, watson2016patterns}) and
objects (e.g. spatial contextual associations \citep{aminoff2007parahippocampal,
aminoff2013role}).

>>>>

% intro
Results of the AO contrasts consistently yielded significant clusters spatially
constrained to the anterior part of the PPA group overlap [and to the anterior
part of significant clusters of the AV contrasts].
% PPA might have submodules
Previous studies provide evidence that the PPA can be devided into functionally
subregions that might process different stimulus features [during visual scene
perception].
% posterior: functionality
The posterior PPA (pPPA) is functionally more responsive than the anterior PPA
(aPPA) to low-level features of scenes or (abstract) objects
\citep{baldassano2013differential, nasr2014thinking,
rajimehr2011parahippocampal}.
% anterior cIPL is defined using the Eickhoff–Zilles PGp probabilistic
% cytoarchitectonic map
The aPPA is functionally more responsive than pPPA to high-level features of
scenes (e.g. real-word size \citep{park2015parametric}; a scene's abstract
identity/category \citep{marchette2015outside, watson2016patterns}) and objects
(e.g. spatial contextual associations \citep{aminoff2007parahippocampal,
aminoff2013role}).
% connectivity
Moreover, pPPA and aPPA show differences in connectivity profiles.
% posterior
The pPPA is more strongly functionally connected to the occipital
visual cortex than the aPPA \citep{baldassano2013differential,
baldassano2016two}.
% including lateral occipital cortex (LOC) and transverse occipital sulcus (TOS)
% anterior
The aPPA is more strongly functionally connected to portions of the default mode
network, including caudal inferior parietal lobe (cIPL), the restrosplenial
complex (RSC), medial PFC and the lateral surface of the anterior temporal lobe
\citep{baldassano2013differential, baldassano2016two}.
